---
title: "R for Data Science - Final exam"
author: "Caterina Daidone, Paola Galfrascoli, Anastasia Galkina, Muhammad Haroon Shaukat"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1 - Exploratory Data Analysis

```{r echo=F, results='hide'}
library(rwhatsapp)
covfefe_chat <- rwa_read(
  here::here("exam", "covfefe_chat.txt"),
  encoding = "UTF-8"
)
library(dplyr, warn.conflicts = FALSE)
glimpse(covfefe_chat)
```


**Who sent the highest number of messages?**  
Andrea Gilardi sent the highest number of messages: 233.  

```{r}
covfefe_chat %>%  count(author, sort = T) 

```
  
**How many messages were exchanged during December 2022?**  
During December 2022 were exchanged 246 messages.  

```{r}
covfefe_chat %>% 
  mutate(Month = lubridate::month(time, label = FALSE),
         Year = lubridate::year(time), DayMonth = format(as.Date(time), "%y-%m")) %>%
  count(DayMonth) %>%  filter(DayMonth == '22-12')
```
    
**Who sent the first message of the current year? At which time?**  
The first message of the 2023 was sent by Andrea Gilardi at 15:08:43 on 2023-01-04.  

```{r}
covfefe_chat %>% filter(time > '2022-12-31') %>%  slice(1) 
```
    
**On which day did we exchange the highest number of messages? After filtering the corresponding text messages, check their content and try to explain the anomalous behaviour.**  
The highest number of messages was exchanged on the 1st February 2023 (60 messages).

```{r}
covfefe_chat %>% 
  mutate(YearMonthDay = format(as.Date(time), "%y-%m-%d")) %>% count(YearMonthDay, sort = T)
```
  
Most of the messages of this day were exchanged to plan for an aperitif in the evening and a poll was created to count how many people were in. There were difficulties in finding a place where to have it.
```{r}
covfefe_chat %>% 
  mutate(YearMonthDay = format(as.Date(time), "%y-%m-%d")) %>% 
  filter(YearMonthDay == "23-02-01") %>% select(text)
```
    
**How many messages are sent on average per day?**  
15 messages are sent on average per day.  

```{r}
covfefe_chat %>% 
  mutate(YearMonthDay = format(as.Date(time), "%y-%m-%d")) %>%
  count(YearMonthDay) %>% summarise(mean = mean(as.numeric(n))) %>% round()
```
    
**Who sent the highest number of messages which included at least one emoji?**  
Andrea Gilardi sent the highest number of messages (66) which included at least one emoji.  

```{r}
covfefe_chat %>% filter(!vapply(emoji, is.null, logical(1))) %>% count(author, sort = T)
```


**Determine the most common emoji for each author. In case of ties, you can select any of the equally-used emojies.**  
See below the list of authors with their most frequently used emoji. 8 authors have never used an emoji.  

```{r, message=FALSE, warning=F}
library(tidyr)

covfefe_chat%>%
  unnest(c(emoji,emoji_name))%>%
  filter(!is.na(author)& emoji!="NULL")%>%
  group_by(author,emoji)%>%
  reframe(emoji,emoji_name,freq=n())%>%
  group_by(author) %>%
  arrange(desc(freq), .by_group = T) %>%
  distinct() %>%
  slice_head() %>% select(author, emoji_name, freq) %>%
  print(n=23)

```



  
    

<br>

## Exercise 2 - Debugging techniques

**Question 1: Explain why `termplot()` raises a warning message when we pass `mod2` instead of `mod1` and the steps you took / the techniques you used to tackle this problem.**  

First, we run the code provided in the text to create the data of the example and we investigates the output of the `termplot()` function.

```{r echo=T, results='hide'}
set.seed(1)
n <- 10L
x1 <- rnorm(n)
x2 <- seq.int(n)
beta0 <- 0; beta1 <- 1; beta2 <- 2
y <- beta0 + beta1 * x1 + beta2 * x2 + rnorm(n)

(mod1 <- lm(y ~ x1 + x2))
termplot(mod1, ask = FALSE, ylim = "free")

(mod2 <- lm(y ~ x1 + I(1:n)))
termplot(mod2, ask = FALSE, ylim = "free")
```


Then, in order to understand how the function works, we go into the debug mode. Since the `termplot()` function is defined in a base package (`stats`), we cannot use the `browser()` call directly into the function definition. Then, we use the `debug()` function that automatically sets up a `browser()` call at the beginning of the `termplot()` function. (We will not print the entire debug console output for conciseness.)

```{r results='hide', fig.show='hide'}
debug(termplot)
termplot(mod2, ask = FALSE, ylim = "free")
```


In debug mode, we go through the function code using the following debug commands:  
`n`: executes the next step in the function;  
`s`: steps into the next function;  
`f`: finishes execution of the current loop or function;  
`c`: leaves interactive debugging and continues regular execution of the function;  
`q`: stops debugging, terminates the function, and returns to the global workspace.  

The warning message appears because of the following piece of code:
```{r eval=FALSE}
if (any(grepl(":", nmt, fixed = TRUE))) 
        warning("'model' appears to involve interactions: see the help page", 
            domain = NA, immediate. = TRUE)
```

The function `grepl()` identifies the symbol ":" in the object `nmt`, which is the vector of column names of the output of the `predict()` function applied to `mod2` inside `termplot()`. If there are interactions in the model, some of the column names will have the ":" in them (e.g. an interaction between `x1` and `x2` will have its corresponding column name as `x1:x2`). So, this code is intended to create a warning when there are some interactions in the model, but in our case it appears because in `mod2` the second variable is expressed as `I(1:n)`.  




**Question 2: Explain why `termplot()` creates an empty plot when displaying the relationship between `x2 := 1:n` and its predicted values.**  

When selecting the $x$-axis values for the plot, the `termplot()` function adopts a procedure that erroneously picks just the value $1$. More in detail, the function that selects the $x$-axis values is the `carrier()` function, defined inside the `termplot()` itself. Then, by using command `s` in debug mode, we step into this function and see why the code doesn't work for the variable named `I(1:n)`. This function has arguments `term` and `transform`. The second term is equal `FALSE` in our example, while the first one is taken from an object of the form `expression(x1, I(1:n))`, obtained by applying the function `str2expression()` to the column names `x1` and `I(1:n)`. Because of an `if` condition that evaluates the length of the argument `term` being greater than `1L`, the function, after some repeated steps, returns as the $x$-axis values as single number: $1$. The `xlim` argument and the $y$-axis values of the plot are also affected by this result, and the consequence is a plot similar to the output of the following code: 
```{r}
plot(1, -9.361879, type = "l", xlim = c(1,1), ylim = c(-9.361879,  9.361879), ylab="")
```