---
title: "Exercise 2"
author: "Paola Galfrascoli"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 2 - Debugging techniques

**Question 1: Explain why `termplot()` raises a warning message when we pass `mod2` instead of `mod1` and the steps you took / the techniques you used to tackle this problem.**  

First, we run the code provided in the text to create the data of the example and we investigates the output of the `termplot()` function.

```{r echo=T, results='hide'}
set.seed(1)
n <- 10L
x1 <- rnorm(n)
x2 <- seq.int(n)
beta0 <- 0; beta1 <- 1; beta2 <- 2
y <- beta0 + beta1 * x1 + beta2 * x2 + rnorm(n)

(mod1 <- lm(y ~ x1 + x2))
termplot(mod1, ask = FALSE, ylim = "free")

(mod2 <- lm(y ~ x1 + I(1:n)))
termplot(mod2, ask = FALSE, ylim = "free")
```


Then, in order to understand how the function works, we go into the debug mode. Since the `termplot()` function is defined in a base package (`stats`), we cannot use the `browser()` call directly into the function definition. Then, we use the `debug()` function that automatically sets up a `browser()` call at the beginning of the `termplot()` function. (We will not print the entire debug console output for conciseness.)

```{r results='hide', fig.show='hide'}
debug(termplot)
termplot(mod2, ask = FALSE, ylim = "free")
```


In debug mode, we go through the function code using the following debug commands:  
`n`: executes the next step in the function;  
`s`: steps into the next function;  
`f`: finishes execution of the current loop or function;  
`c`: leaves interactive debugging and continues regular execution of the function;  
`q`: stops debugging, terminates the function, and returns to the global workspace.  

The warning message appears because of the following piece of code:
```{r eval=FALSE}
if (any(grepl(":", nmt, fixed = TRUE))) 
        warning("'model' appears to involve interactions: see the help page", 
            domain = NA, immediate. = TRUE)
```

The function `grepl()` identifies the symbol ":" in the object `nmt`, which is the vector of column names of the output of the `predict()` function applied to `mod2` inside `termplot()`. If there are interactions in the model, some of the column names will have the ":" in them (e.g. an interaction between `x1` and `x2` will have its corresponding column name as `x1:x2`). So, this code is intended to create a warning when there are some interactions in the model, but in our case it appears because in `mod2` the second variable is expressed as `I(1:n)`.  




**Explain why `termplot()` creates an empty plot when displaying the relationship between `x2 := 1:n` and its predicted values.**  

