---
title: "Exercise 1"
author: "Paola Galfrascoli"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1 - Exploratory Data Analysis

```{r echo=F, results='hide'}
library(rwhatsapp)
covfefe_chat <- rwa_read(
  here::here("exam", "covfefe_chat.txt"),
  encoding = "UTF-8"
)
library(dplyr, warn.conflicts = FALSE)
glimpse(covfefe_chat)
```


**Who sent the highest number of messages?**  
Andrea Gilardi sent the highest number of messages: 233.  

```{r}
covfefe_chat %>%  count(author, sort = T) 

```
  
**How many messages were exchanged during December 2022?**  
During December 2022 were exchanged 246 messages.  

```{r}
covfefe_chat %>% 
  mutate(Month = lubridate::month(time, label = FALSE),
         Year = lubridate::year(time), DayMonth = format(as.Date(time), "%y-%m")) %>%
  count(DayMonth) %>%  filter(DayMonth == '22-12')
```
    
**Who sent the first message of the current year? At which time?**  
The first message of the 2023 was sent by Andrea Gilardi at 15:08:50.  

```{r}
covfefe_chat %>% filter(time > '2022-12-31') %>%  slice(1) 
```
    
**On which day did we exchange the highest number of messages? After filtering the corresponding text messages, check their content and try to explain the anomalous behaviour.**  
The highest number of messages was exchanged on the 1st February 2023 (60 messages).

```{r}
covfefe_chat %>% 
  mutate(YearMonthDay = format(as.Date(time), "%y-%m-%d")) %>% count(YearMonthDay, sort = T)
```
  
Most of the messages of this day were exchanged to plan for an aperitif in the evening and a poll was created to count how many people were in. There were difficulties in finding a place where to have it.
```{r}
covfefe_chat %>% 
  mutate(YearMonthDay = format(as.Date(time), "%y-%m-%d")) %>% 
  filter(YearMonthDay == "23-02-01") %>% select(text)
```
    
**How many messages are sent on average per day?**  
14.5045 are sent on average per day.  

```{r}
covfefe_chat %>% 
  mutate(YearMonthDay = format(as.Date(time), "%y-%m-%d")) %>%
  count(YearMonthDay) %>% summarise(mean = mean(n))
```
    
**Who sent the highest number of messages which included at least one emoji?**  
Andrea Gilardi sent the highest number of messages (66) which included at least one emoji.  

```{r}
covfefe_chat %>% filter(!vapply(emoji, is.null, logical(1))) %>% count(author, sort = T)
```
